Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-18 talk/pepm2011/paper.tex
more nonsense

\begin{lstlisting}[mathescape,xleftmargin=20pt]
guard_class($p_{5}$, BoxedInteger)
$i_{7}$ = get($p_{5}$, intval)
# inside BoxedInteger.add
guard_class($p_{6}$, BoxedInteger)
# inside BoxedInteger.add__int
$i_{8}$ = get($p_{6}$, intval)
$i_{9}$ = int_add($i_{7}$, $i_{8}$)
\end{lstlisting}

>>>>

\begin{lstlisting}[mathescape,xleftmargin=20pt]
guard_class($p_{5}$, BoxedInteger)
# inside BoxedInteger.add
$i_{7}$ = get($p_{5}$, intval)
guard_class($p_{6}$, BoxedInteger)
# inside BoxedInteger.add__int
$i_{8}$ = get($p_{6}$, intval)
$i_{9}$ = int_add($i_{7}$, $i_{8}$)
\end{lstlisting}
